---
title: "CancerCovid Endocrine Tx Preliminary Analyses"
author: "Nicola Barclay"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, echo=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
```

### Cancer/ Covid Breast and Prostate Cancer Endocrine Treatment Preliminary Analyses

## 1. Incidence of the use of endocrine treatments for breast and prostate cancer in the general population. 

Denominator cohorts specified in the Incidence/Prevalence package with 0 days prior history:

```{r, echo=FALSE}
Denominator_counts_0
```

Denominator cohorts specified in the Incidence/Prevalence package with 0 days prior history:

```{r, echo=FALSE}
Denominator_counts_365
```

# 1a. Incidence Rates of Endocrine Treatments for Breast or Prostate Cancer in Quarters 
# in the General Population Before and After COVID-19 Lockdown 
# (0 days prior history, 90 days washout)

```{r, echo=FALSE}
inc_yrs_plot <- inc_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "AromataseInhibitors" ~ "Aromatase Inhibitors",
                             outcome_cohort_name == "AromataseInhibitors_withGnRHAgonistsOrAntagonists" ~ "Aromatase Inhibitors with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "First_generation_antiandrogens" ~ "First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists_with1stGenADT" ~ "GnRH Agonists with First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists" ~ "GnRH Agonists",
                             outcome_cohort_name == "GNRH_LHRH_antagonists" ~ "GnRH Antagonists",
                             outcome_cohort_name == "Second_generation_antiandrogens" ~ "Second Generation Antiandrogens",
                             outcome_cohort_name == "Tamoxifen_withGnRHAgonistsOrAntagonists" ~ "Tamoxifen with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen" ~ "Tamoxifen")) %>% 
  as.data.frame()

inc_yrs_plot <- 
  ggplot(inc_yrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  scale_y_continuous(limits = c(0, NA)) +
  scale_x_date(date_labels="%Y",date_breaks  ="1 year") +
  ggtitle("Incidence Rates of Endocrine Treatments for Breast or Prostate Cancer in Quarters 
          in the General Population Before and After COVID-19 Lockdown 
          (0 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_yrs_plot

```


# 1b. Incidence Rates of Endocrine Treatments for Breast or Prostate Cancer in Quarters 
# in the General Population Before and After COVID-19 Lockdown 
# (0 days prior history, 0 days washout)

```{r, echo=FALSE}
inc_yrs_plot <- inc_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "AromataseInhibitors" ~ "Aromatase Inhibitors",
                             outcome_cohort_name == "AromataseInhibitors_withGnRHAgonistsOrAntagonists" ~ "Aromatase Inhibitors with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "First_generation_antiandrogens" ~ "First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists_with1stGenADT" ~ "GnRH Agonists with First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists" ~ "GnRH Agonists",
                             outcome_cohort_name == "GNRH_LHRH_antagonists" ~ "GnRH Antagonists",
                             outcome_cohort_name == "Second_generation_antiandrogens" ~ "Second Generation Antiandrogens",
                             outcome_cohort_name == "Tamoxifen_withGnRHAgonistsOrAntagonists" ~ "Tamoxifen with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen" ~ "Tamoxifen")) %>% 
  as.data.frame()

inc_yrs_plot <- 
  ggplot(inc_yrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  scale_y_continuous(limits = c(0, NA)) +
  scale_x_date(date_labels="%Y",date_breaks  ="1 year") +
  ggtitle("Incidence Rates of Endocrine Treatments for Breast or Prostate Cancer in Quarters 
          in the General Population Before and After COVID-19 Lockdown 
          (0 days prior history, 0 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_yrs_plot

```



# 1c. Incidence Rates of Endocrine Treatments for Breast or Prostate Cancer in Quarters 
# in the General Population Before and After COVID-19 Lockdown 
# (365 days prior history, 90 days washout)

```{r, echo=FALSE}
inc_yrs_plot <- inc_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "AromataseInhibitors" ~ "Aromatase Inhibitors",
                             outcome_cohort_name == "AromataseInhibitors_withGnRHAgonistsOrAntagonists" ~ "Aromatase Inhibitors with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "First_generation_antiandrogens" ~ "First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists_with1stGenADT" ~ "GnRH Agonists with First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists" ~ "GnRH Agonists",
                             outcome_cohort_name == "GNRH_LHRH_antagonists" ~ "GnRH Antagonists",
                             outcome_cohort_name == "Second_generation_antiandrogens" ~ "Second Generation Antiandrogens",
                             outcome_cohort_name == "Tamoxifen_withGnRHAgonistsOrAntagonists" ~ "Tamoxifen with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen" ~ "Tamoxifen")) %>% 
  as.data.frame()

inc_yrs_plot <- 
  ggplot(inc_yrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  scale_y_continuous(limits = c(0, NA)) +
  scale_x_date(date_labels="%Y",date_breaks  ="1 year") +
  ggtitle("Incidence Rates of Endocrine Treatments for Breast or Prostate Cancer in Quarters 
          in the General Population Before and After COVID-19 Lockdown 
          (365 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_yrs_plot

```


# 1d. Incidence Rates of Endocrine Treatments for Breast or Prostate Cancer in Quarters 
# in the General Population Before and After COVID-19 Lockdown 
# (365 days prior history, 0 days washout)

```{r, echo=FALSE}
inc_yrs_plot <- inc_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "AromataseInhibitors" ~ "Aromatase Inhibitors",
                             outcome_cohort_name == "AromataseInhibitors_withGnRHAgonistsOrAntagonists" ~ "Aromatase Inhibitors with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "First_generation_antiandrogens" ~ "First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists_with1stGenADT" ~ "GnRH Agonists with First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists" ~ "GnRH Agonists",
                             outcome_cohort_name == "GNRH_LHRH_antagonists" ~ "GnRH Antagonists",
                             outcome_cohort_name == "Second_generation_antiandrogens" ~ "Second Generation Antiandrogens",
                             outcome_cohort_name == "Tamoxifen_withGnRHAgonistsOrAntagonists" ~ "Tamoxifen with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen" ~ "Tamoxifen")) %>% 
  as.data.frame()

inc_yrs_plot <- 
  ggplot(inc_yrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  scale_y_continuous(limits = c(0, NA)) +
  scale_x_date(date_labels="%Y",date_breaks  ="1 year") +
  ggtitle("Incidence Rates of Endocrine Treatments for Breast or Prostate Cancer in Quarters 
          in the General Population Before and After COVID-19 Lockdown 
          (365 days prior history, 0 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_yrs_plot

```



## 2. Incidence of the use of endocrine treatments for breast cancer in breast cancer patients

Breast cancer strata cohorts specified in the Incidence/Prevalence package with 0 days prior history:

```{r, echo=FALSE}
Breast_strata_counts_0
```

Breast cancer strata cohorts specified in the Incidence/Prevalence package with 365 days prior history:
```{r, echo=FALSE}
Breast_strata_counts_365
```

# 2a. Incidence Rates of Endocrine Treatments for Breast Cancer in Quarters 
# in Breast Cancer Patients Before and After COVID-19 Lockdown 
# (0 days prior history, 90 days washout)

```{r, echo=FALSE}
inc_qrs_plot <- IncTxBreast_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  filter(outcome_cohort_name %in% c("AromataseInhibitors", "AromataseInhibitors_withGnRHAgonistsOrAntagonists","Tamoxifen_withGnRHAgonistsOrAntagonists","Tamoxifen")) %>%
  mutate(outcome = case_when(outcome_cohort_name == "AromataseInhibitors" ~ "Aromatase Inhibitors",
                             outcome_cohort_name == "AromataseInhibitors_withGnRHAgonistsOrAntagonists" ~ "Aromatase Inhibitors with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen_withGnRHAgonistsOrAntagonists" ~ "Tamoxifen with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen" ~ "Tamoxifen")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
 # scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  
  ggtitle("Incidence Rates of Endocrine Treatments in Quarters in Breast Cancer 
  Patients Before and After COVID-19 Lockdown 
  (0 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```



# 2b. Incidence Rates of Endocrine Treatments for Breast Cancer in Quarters 
# in Breast Cancer Patients Before and After COVID-19 Lockdown 
# (0 days prior history, 0 days washout)

```{r, echo=FALSE}
inc_qrs_plot <- IncTxBreast_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  filter(outcome_cohort_name %in% c("AromataseInhibitors", "AromataseInhibitors_withGnRHAgonistsOrAntagonists","Tamoxifen_withGnRHAgonistsOrAntagonists","Tamoxifen")) %>%
  mutate(outcome = case_when(outcome_cohort_name == "AromataseInhibitors" ~ "Aromatase Inhibitors",
                             outcome_cohort_name == "AromataseInhibitors_withGnRHAgonistsOrAntagonists" ~ "Aromatase Inhibitors with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen_withGnRHAgonistsOrAntagonists" ~ "Tamoxifen with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen" ~ "Tamoxifen")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
 # scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  
  ggtitle("Incidence Rates of Endocrine Treatments in Quarters in Breast Cancer 
  Patients Before and After COVID-19 Lockdown 
  (0 days prior history, 0 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


# 2c. Incidence Rates of Endocrine Treatments for Breast Cancer in Quarters 
# in Breast Cancer Patients Before and After COVID-19 Lockdown 
# (365 days prior history, 90 days washout)

```{r, echo=FALSE}
inc_qrs_plot <- IncTxBreast_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  filter(outcome_cohort_name %in% c("AromataseInhibitors", "AromataseInhibitors_withGnRHAgonistsOrAntagonists","Tamoxifen_withGnRHAgonistsOrAntagonists","Tamoxifen")) %>%
  mutate(outcome = case_when(outcome_cohort_name == "AromataseInhibitors" ~ "Aromatase Inhibitors",
                             outcome_cohort_name == "AromataseInhibitors_withGnRHAgonistsOrAntagonists" ~ "Aromatase Inhibitors with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen_withGnRHAgonistsOrAntagonists" ~ "Tamoxifen with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen" ~ "Tamoxifen")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
 # scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  
  ggtitle("Incidence Rates of Endocrine Treatments in Quarters in Breast Cancer 
  Patients Before and After COVID-19 Lockdown 
  (365 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```



# 2d. Incidence Rates of Endocrine Treatments for Breast Cancer in Quarters 
# in Breast Cancer Patients Before and After COVID-19 Lockdown 
# (365 days prior history, 0 days washout)

```{r, echo=FALSE}
inc_qrs_plot <- IncTxBreast_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  filter(outcome_cohort_name %in% c("AromataseInhibitors", "AromataseInhibitors_withGnRHAgonistsOrAntagonists","Tamoxifen_withGnRHAgonistsOrAntagonists","Tamoxifen")) %>%
  mutate(outcome = case_when(outcome_cohort_name == "AromataseInhibitors" ~ "Aromatase Inhibitors",
                             outcome_cohort_name == "AromataseInhibitors_withGnRHAgonistsOrAntagonists" ~ "Aromatase Inhibitors with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen_withGnRHAgonistsOrAntagonists" ~ "Tamoxifen with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen" ~ "Tamoxifen")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
 # scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  
  ggtitle("Incidence Rates of Endocrine Treatments in Quarters in Breast Cancer 
  Patients Before and After COVID-19 Lockdown 
  (365 days prior history, 0 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


## 3. Incidence of the use of endocrine treatments for prostate cancer in prostate cancer patients

Prostate cancer strata cohorts specified in the Incidence/Prevalence package with 0 days prior history:

```{r, echo=FALSE}
Prostate_strata_counts_0
```

Prostate cancer strata cohorts specified in the Incidence/Prevalence package with 365 days prior history:

```{r, echo=FALSE}
Prostate_strata_counts_365
```


# 3a. Incidence Rates of Endocrine Treatments for Prostate Cancer in Quarters 
# in Prostate Cancer Patients Before and After COVID-19 Lockdown 
# (0 days prior history, 90 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxProstate_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  filter(outcome_cohort_name %in% c("First_generation_antiandrogens", "GNRH_Agonists_with1stGenADT","GNRH_Agonists","GNRH_LHRH_antagonists", "Second_generation_antiandrogens")) %>%
  mutate(outcome = case_when(outcome_cohort_name == "First_generation_antiandrogens" ~ "First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists_with1stGenADT" ~ "GnRH Agonists with First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists" ~ "GnRH Agonists",
                             outcome_cohort_name == "GNRH_LHRH_antagonists" ~ "GnRH Antagonists",
                             outcome_cohort_name == "Second_generation_antiandrogens" ~ "Second Generation Antiandrogens")) %>% 
  as.data.frame()



inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatments in Quarters in Prostate Cancer 
          Patients Before and After COVID-19 Lockdown 
          (0 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


# 3b. Incidence Rates of Endocrine Treatments for Prostate Cancer in Quarters 
# in Prostate Cancer Patients Before and After COVID-19 Lockdown 
# (0 days prior history, 0 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxProstate_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  filter(outcome_cohort_name %in% c("First_generation_antiandrogens", "GNRH_Agonists_with1stGenADT","GNRH_Agonists","GNRH_LHRH_antagonists", "Second_generation_antiandrogens")) %>%
  mutate(outcome = case_when(outcome_cohort_name == "First_generation_antiandrogens" ~ "First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists_with1stGenADT" ~ "GnRH Agonists with First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists" ~ "GnRH Agonists",
                             outcome_cohort_name == "GNRH_LHRH_antagonists" ~ "GnRH Antagonists",
                             outcome_cohort_name == "Second_generation_antiandrogens" ~ "Second Generation Antiandrogens")) %>% 
  as.data.frame()



inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatments in Quarters in Prostate Cancer 
          Patients Before and After COVID-19 Lockdown 
          (0 days prior history, 0 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```

# 3c. Incidence Rates of Endocrine Treatments for Prostate Cancer in Quarters 
# in Prostate Cancer Patients Before and After COVID-19 Lockdown 
# (365 days prior history, 90 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxProstate_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  filter(outcome_cohort_name %in% c("First_generation_antiandrogens", "GNRH_Agonists_with1stGenADT","GNRH_Agonists","GNRH_LHRH_antagonists", "Second_generation_antiandrogens")) %>%
  mutate(outcome = case_when(outcome_cohort_name == "First_generation_antiandrogens" ~ "First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists_with1stGenADT" ~ "GnRH Agonists with First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists" ~ "GnRH Agonists",
                             outcome_cohort_name == "GNRH_LHRH_antagonists" ~ "GnRH Antagonists",
                             outcome_cohort_name == "Second_generation_antiandrogens" ~ "Second Generation Antiandrogens")) %>% 
  as.data.frame()



inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatments in Quarters in Prostate Cancer 
          Patients Before and After COVID-19 Lockdown 
          (365 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```

# 3d. Incidence Rates of Endocrine Treatments for Prostate Cancer in Quarters 
# in Prostate Cancer Patients Before and After COVID-19 Lockdown 
# (365 days prior history, 0 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxProstate_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  filter(outcome_cohort_name %in% c("First_generation_antiandrogens", "GNRH_Agonists_with1stGenADT","GNRH_Agonists","GNRH_LHRH_antagonists", "Second_generation_antiandrogens")) %>%
  mutate(outcome = case_when(outcome_cohort_name == "First_generation_antiandrogens" ~ "First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists_with1stGenADT" ~ "GnRH Agonists with First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists" ~ "GnRH Agonists",
                             outcome_cohort_name == "GNRH_LHRH_antagonists" ~ "GnRH Antagonists",
                             outcome_cohort_name == "Second_generation_antiandrogens" ~ "Second Generation Antiandrogens")) %>% 
  as.data.frame()



inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatments in Quarters in Prostate Cancer 
          Patients Before and After COVID-19 Lockdown 
          (0 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```



## 4. Incidence of endocrine treatment-related outcomes for breast cancer patients 
## on Aromatase Inhibitors

Breast cancer patients on aromatase inhibitors strata cohorts specified in the Incidence/Prevalence package with 0 days prior history:

```{r, echo=FALSE}
Breast_AI_counts_0
```


Breast cancer patients on aromatase inhibitors strata cohorts specified in the Incidence/Prevalence package with 365 days prior history:

```{r, echo=FALSE}
Breast_AI_counts_365
```

# 4a. Incidence Rates of endocrine treatment-related outcomes for breast cancer patients 
# on Aromatase Inhibitors in Quarters Before and After COVID-19 Lockdown 
# (0 days prior history, 90 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesBreastAI_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Breast Cancer Patients on Aromatase Inhibitors Before and After 
          COVID-19 Lockdown (0 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


# 4b. Incidence Rates of endocrine treatment-related outcomes for breast cancer patients 
# on Aromatase Inhibitors in Quarters Before and After COVID-19 Lockdown 
# (0 days prior history, 0 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesBreastAI_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Breast Cancer Patients on Aromatase Inhibitors Before and After 
          COVID-19 Lockdown (0 days prior history, 0 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


# 4c. Incidence Rates of endocrine treatment-related outcomes for breast cancer patients 
# on Aromatase Inhibitors in Quarters Before and After COVID-19 Lockdown 
# (365 days prior history, 90 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesBreastAI_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Breast Cancer Patients on Aromatase Inhibitors Before and After 
          COVID-19 Lockdown (365 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


# 4d. Incidence Rates of endocrine treatment-related outcomes for breast cancer patients 
# on Aromatase Inhibitors in Quarters Before and After COVID-19 Lockdown 
# (365 days prior history, 0 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesBreastAI_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Breast Cancer Patients on Aromatase Inhibitors Before and After 
          COVID-19 Lockdown (365 days prior history, 0 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```



## 5. Incidence of endocrine treatment-related outcomes for breast cancer patients 
## on Tamoxifen

Breast cancer patients on tamoxifen strata cohorts specified in the Incidence/Prevalence package with 0 days prior history:

```{r, echo=FALSE}
Breast_tamoxifen_counts_0
```


Breast cancer patients on tamoxifen strata cohorts specified in the Incidence/Prevalence package with 365 days prior history:

```{r, echo=FALSE}
Breast_tamoxifen_counts_365
```

# 5a. Incidence Rates of endocrine treatment-related outcomes for breast cancer patients 
# on Tamoxifen in Quarters Before and After COVID-19 Lockdown 
# (0 days prior history, 90 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesBreastTAM_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Breast Cancer Patients on Tamoxifen Before and After 
          COVID-19 Lockdown (0 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


# 5b. Incidence Rates of endocrine treatment-related outcomes for breast cancer patients 
# on Tamoxifen in Quarters Before and After COVID-19 Lockdown 
# (0 days prior history, 0 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesBreastTAM_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Breast Cancer Patients on Tamoxifen Before and After 
          COVID-19 Lockdown (0 days prior history, 0 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


# 5c. Incidence Rates of endocrine treatment-related outcomes for breast cancer patients 
# on Tamoxifen in Quarters Before and After COVID-19 Lockdown 
# (365 days prior history, 90 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesBreastTAM_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Breast Cancer Patients on Tamoxifen Before and After 
          COVID-19 Lockdown (365 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


# 5d. Incidence Rates of endocrine treatment-related outcomes for breast cancer patients 
# on Tamoxifen in Quarters Before and After COVID-19 Lockdown 
# (365 days prior history, 0 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesBreastTAM_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Breast Cancer Patients on Tamoxifen Before and After 
          COVID-19 Lockdown (365 days prior history, 0 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```





## 6. Incidence of endocrine treatment-related outcomes for prostate cancer patients 
## on endocrine treatments

Prostate cancer patients on endocrine treatments strata cohorts specified in the Incidence/Prevalence package with 0 days prior history:

```{r, echo=FALSE}
Prostate_endocrine_counts_0
```


Prostate cancer patients on endocrine treatments strata cohorts specified in the Incidence/Prevalence package with 365 days prior history:

```{r, echo=FALSE}
Prostate_endocrine_counts_365
```

# 6a. Incidence Rates of endocrine treatment-related outcomes for prostate cancer patients 
# on endocrine treatments in Quarters Before and After COVID-19 Lockdown 
# (0 days prior history, 90 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesProstate_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Prostate Cancer Patients on Endocrine Treatments Before and After 
          COVID-19 Lockdown (0 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


# 6b. Incidence Rates of endocrine treatment-related outcomes for prostate cancer patients 
# on endocrine treatments in Quarters Before and After COVID-19 Lockdown 
# (0 days prior history, 0 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesProstate_0 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Prostate Cancer Patients on Endocrine Treatments Before and After 
          COVID-19 Lockdown (0 days prior history, 0 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


# 6c. Incidence Rates of endocrine treatment-related outcomes for breast cancer patients 
# on endocrine treatments in Quarters Before and After COVID-19 Lockdown 
# (365 days prior history, 90 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesProstate_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 90) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Prostate Cancer Patients on Endocrine Treatments Before and After 
          COVID-19 Lockdown (365 days prior history, 90 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```


# 6d. Incidence Rates of endocrine treatment-related outcomes for prostate cancer patients 
# on endocrine treatments in Quarters Before and After COVID-19 Lockdown 
# (365 days prior history, 0 days washout)

```{r, echo=FALSE}

inc_qrs_plot <- IncTxOutcomesProstate_365 %>%  
  filter(denominator_cohort_id == 1) %>%
  filter(analysis_outcome_washout == 0) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months") +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters 
          in Prostate Cancer Patients on Endocrine Treatments Before and After 
          COVID-19 Lockdown (365 days prior history, 0 days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 12))

inc_qrs_plot
```