---
title: "CancerCovid Endocrine Tx Preliminary Analyses"
author: "Nicola Barclay"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, echo=FALSE}
#knitr::opts_chunk$set(echo = FALSE, fig.width=20, fig.height=10) 
```

### Cancer/ Covid Breast and Prostate Cancer Endocrine Treatment Preliminary Analyses

#### 1. Incidence of the use of endocrine treatments for breast and prostate cancer in the general population. 

Denominator cohorts specified in the Incidence/Prevalence package with 365 days prior history:


```{r, echo=FALSE}
load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/1_EndocrineTxDenom/Denominator_counts.RData")
Denominator_counts 
```



#### 1. Incidence Rates of Endocrine Treatments for Breast or Prostate Cancer in Quarters 
#### in the General Population Before and After COVID-19 Lockdown 
#### (365 days prior history, Inf days washout)

``````{r, echo=FALSE, fig.width=20, fig.height=10}
 load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/1_EndocrineTxDenom/IncTxDenom.RData")


 library(here)

 library(dplyr)
 library(readr)

 library(tidyr)
 library(stringr)

 library(ggplot2)

 inc_qrs_plot <- inc %>%
   filter(denominator_cohort_id == 1) %>%
   filter(analysis_interval == "quarters") %>%
   mutate(outcome = case_when(outcome_cohort_name == "AromataseInhibitors" ~ "Aromatase Inhibitors",
                              outcome_cohort_name == "AromataseInhibitors_withGnRHAgonistsOrAntagonists" ~ "Aromatase Inhibitors with GnRH Agonists Or Antagonists",
                              outcome_cohort_name == "First_generation_antiandrogens" ~ "First Generation Antiandrogens",
                              outcome_cohort_name == "GNRH_Agonists_with1stGenADT" ~ "GnRH Agonists with First Generation Antiandrogens",
                              outcome_cohort_name == "GNRH_Agonists" ~ "GnRH Agonists",
                              outcome_cohort_name == "GNRH_LHRH_antagonists" ~ "GnRH Antagonists",
                              outcome_cohort_name == "Second_generation_antiandrogens" ~ "Second Generation Antiandrogens",
                              outcome_cohort_name == "Tamoxifen_withGnRHAgonistsOrAntagonists" ~ "Tamoxifen with GnRH Agonists Or Antagonists",
                              outcome_cohort_name == "Tamoxifen" ~ "Tamoxifen")) %>%
   as.data.frame()

 inc_qrs_plot <-
   ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                            ymin = incidence_100000_pys_95CI_lower,
                            ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome,show.legend = FALSE)) +
   geom_point() + geom_line() +
   geom_errorbar(width=0) +
   scale_y_continuous(limits = c(0, 150)) +
   scale_x_date(date_labels="%b %Y",date_breaks  ="3 months", expand = c(0.05,0.05)) +
   facet_wrap(~outcome, nrow=2, scales = "free_y", labeller = label_wrap_gen()) +
    ggtitle("Incidence Rates of Endocrine Treatments for Breast or Prostate Cancer \nin Quarters in the General Population Before and After COVID-19 Lockdown (365 days prior history, Inf washout)") +
   labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100,000 person-years") +
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
   geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
   theme(plot.title = element_text(size = 10))+
 theme(legend.position = "none")

 inc_qrs_plot

```





### 2. Incidence of the use of endocrine treatments for breast cancer in breast cancer patients

Breast cancer strata cohorts specified in the Incidence/Prevalence package:

```{r, echo=FALSE}
load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/2_EndocrineTxCancer/Breast_strata_counts.Rdata")

Breast_strata_counts
```

#### 2a. Incidence Rates of Endocrine Treatments for Breast Cancer in Quarters 
#### in Breast Cancer Patients Before and After COVID-19 Lockdown 
#### (365 days prior history, Inf days washout)

```{r, echo=FALSE, out.width="100%"}
load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/2_EndocrineTxCancer/IncTxBreast.RData")

inc_qrs_plot <- IncTxBreast %>%  
  filter(denominator_cohort_id == 2) %>% 
  filter(analysis_interval == "quarters") %>%
  filter(outcome_cohort_name %in% c("AromataseInhibitors", "AromataseInhibitors_withGnRHAgonistsOrAntagonists","Tamoxifen_withGnRHAgonistsOrAntagonists","Tamoxifen")) %>%
  mutate(outcome = case_when(outcome_cohort_name == "AromataseInhibitors" ~ "Aromatase Inhibitors",
                             outcome_cohort_name == "AromataseInhibitors_withGnRHAgonistsOrAntagonists" ~ "Aromatase Inhibitors with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen_withGnRHAgonistsOrAntagonists" ~ "Tamoxifen with GnRH Agonists Or Antagonists",
                             outcome_cohort_name == "Tamoxifen" ~ "Tamoxifen")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
 # scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months", expand = c(0.05, 0.05)) +
  facet_wrap(~outcome, nrow=2, scales = "free_y", labeller = label_wrap_gen()) +
    ggtitle("Incidence Rates of Endocrine Treatments in Quarters in Breast Cancer Patients \nBefore and After COVID-19 Lockdown (365 days prior history, Inf days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100,000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 10))+
 theme(legend.position = "none")

inc_qrs_plot
```





### 3. Incidence of the use of endocrine treatments for prostate cancer in prostate cancer patients

Prostate cancer strata cohorts specified in the Incidence/Prevalence package with 365 days prior history:

```{r, echo=FALSE}
 load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/2_EndocrineTxCancer/Prostate_strata_counts.RData")
Prostate_strata_counts
```


#### 3a. Incidence Rates of Endocrine Treatments for Prostate Cancer in Quarters 
#### in Prostate Cancer Patients Before and After COVID-19 Lockdown 
#### (365 days prior history, Inf days washout)

```{r, echo=FALSE, out.width="100%"}
load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/2_EndocrineTxCancer/IncTxProstate.RData")
inc_qrs_plot <- IncTxProstate %>%  
  filter(denominator_cohort_id == 1) %>% 
  filter(analysis_interval == "quarters") %>%
  filter(outcome_cohort_name %in% c("First_generation_antiandrogens", "GNRH_Agonists_with1stGenADT","GNRH_Agonists","GNRH_LHRH_antagonists", "Second_generation_antiandrogens")) %>%
  mutate(outcome = case_when(outcome_cohort_name == "First_generation_antiandrogens" ~ "First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists_with1stGenADT" ~ "GnRH Agonists with First Generation Antiandrogens",
                             outcome_cohort_name == "GNRH_Agonists" ~ "GnRH Agonists",
                             outcome_cohort_name == "GNRH_LHRH_antagonists" ~ "GnRH Antagonists",
                             outcome_cohort_name == "Second_generation_antiandrogens" ~ "Second Generation Antiandrogens")) %>% 
  as.data.frame()



inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months", expand = c(0.05,0.05)) +
  facet_wrap(~outcome, nrow=2, scales = "free_y", labeller = label_wrap_gen()) +
  ggtitle("Incidence Rates of Endocrine Treatments in Quarters in Prostate Cancer Patients \nBefore and After COVID-19 Lockdown (365 days prior history, Inf days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100,000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 10))+
 theme(legend.position = "none")

inc_qrs_plot
```




### 4. Incidence of endocrine treatment-related outcomes for breast cancer patients 
### on Aromatase Inhibitors

Breast cancer patients on aromatase inhibitors strata cohorts specified in the Incidence/Prevalence package with 365 days prior history:

```{r, echo=FALSE, out.width="100%"}
load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/3_OsteoDx/Breast_AI_counts.RData")
Breast_AI_counts
```


#### 4. Incidence Rates of endocrine treatment-related outcomes for breast cancer patients 
#### on Aromatase Inhibitors in Quarters Before and After COVID-19 Lockdown 
#### (365 days prior history, Inf days washout)

```{r, echo=FALSE, out.width="100%"}
load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/3_OsteoDx/IncTxOutcomesBreastAI.RData")

inc_qrs_plot <- IncTxOutcomesBreastAI %>%  
  filter(denominator_cohort_id == 2) %>%
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months", expand = c(0.05,0.05)) +
  facet_wrap(~outcome, nrow=2, scales = "free_y", labeller = label_wrap_gen()) +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters in Breast Cancer Patients \non Aromatase Inhibitors Before and After COVID-19 Lockdown (365 days prior history, Inf days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100,000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 10))+
 theme(legend.position = "none")

inc_qrs_plot
```




### 5. Incidence of endocrine treatment-related outcomes for breast cancer patients 
### on Tamoxifen

Breast cancer patients on tamoxifen strata cohorts specified in the Incidence/Prevalence package with 365 days prior history:

```{r, echo=FALSE}
load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/3_OsteoDx/Breast_tamoxifen_counts.RData")
Breast_tamoxifen_counts
```


#### 5a. Incidence Rates of endocrine treatment-related outcomes for breast cancer patients 
#### on Tamoxifen in Quarters Before and After COVID-19 Lockdown 
#### (365 days prior history, Inf days washout)

```{r, echo=FALSE, out.width="100%"}
load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/3_OsteoDx/IncTxOutcomesBreastTAM.RData")
inc_qrs_plot <- IncTxOutcomesBreastTAM %>%  
  filter(denominator_cohort_id == 2) %>%
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months", expand = c(0.05,0.05)) +
  facet_wrap(~outcome, nrow=2, scales = "free_y", labeller = label_wrap_gen()) +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters in Breast Cancer Patients \non Tamoxifen Before and After COVID-19 Lockdown (365 days prior history, Inf days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100,000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 10))+
 theme(legend.position = "none")

inc_qrs_plot
```



### 6. Incidence of endocrine treatment-related outcomes for prostate cancer patients 
### on endocrine treatments

Prostate cancer patients on endocrine treatments strata cohorts specified in the Incidence/Prevalence package with 0/365 days prior history:

```{r, echo=FALSE}
load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/3_OsteoDx/Prostate_endocrine_counts.RData")
Prostate_endocrine_counts
```


#### 6a. Incidence Rates of endocrine treatment-related outcomes for prostate cancer patients 
#### on endocrine treatments in Quarters Before and After COVID-19 Lockdown 
#### (365 days prior history, Inf days washout)

```{r, echo=FALSE, out.width="100%"}
load("~/R/CancerCovidEndocrineTx/Results/CPRDGold_202207/3_OsteoDx/IncTxOutcomesProstate.RData")
inc_qrs_plot <- IncTxOutcomesProstate %>%  
  filter(denominator_cohort_id == 1) %>% 
  filter(analysis_interval == "quarters") %>%
  mutate(outcome = case_when(outcome_cohort_name == "Bisphosphonates" ~ "Bisphosphonates",
                             outcome_cohort_name == "Bone Fracture" ~ "Bone Fracture",
                             outcome_cohort_name == "Denosumab" ~ "Denosumab",
                             outcome_cohort_name == "Osteopenia" ~ "Osteopenia",
                             outcome_cohort_name == "Osteoporosis" ~ "Osteoporosis")) %>% 
  as.data.frame()

inc_qrs_plot <- 
  ggplot(inc_qrs_plot, aes(x = incidence_start_date, y=incidence_100000_pys,
                           ymin = incidence_100000_pys_95CI_lower,
                           ymax = incidence_100000_pys_95CI_upper, color=outcome, group=outcome)) +
  geom_point() + geom_line() +
  geom_errorbar(width=0) +
  #scale_y_continuous(limits = c(0, 150)) +
  scale_x_date(date_labels="%b %Y",date_breaks  ="3 months", expand = c(0.05,0.05)) +
  facet_wrap(~outcome, nrow=2, scales = "free_y", labeller = label_wrap_gen()) +
  ggtitle("Incidence Rates of Endocrine Treatment-Related Outcomes in Quarters in Prostate Cancer Patients \non Endocrine Treatments Before and After COVID-19 Lockdown (365 days prior history, Inf days washout)") +
  labs(colour = "Endocrine Treatment", x="Time" , y="Incidence per 100,000 person-years") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept=as.numeric(as.Date(c("2020-03-23"))),linetype=2, color="red") +
  theme(plot.title = element_text(size = 10))+
 theme(legend.position = "none")

inc_qrs_plot
```

### Questions for the team:

#### 1. Are we interested in the prevalence of these drugs over time? Or just how COVID affected new prescriptions (incidence)?

#### 2. What could account for the decreasing trend in incidence of these drugs? No policy changes over time.
- potential regional differences
- potential reduction in cancers over time (though can not find data on this)
- potential increase in use of other treatments

#### 3. Are we interested in forecasting trends across the COVID period based on these data?
- possibly not due to the decreasing trend

#### 4. Are we interested in running ARIMA time-series analsyes?
- this method can account for aut-correlation between data points, seasonality, other time trends

#### 5. Are we interested in performing a large scale characterisation of these cohorts?
- breast / prostate cancer patients
- breast cancer patients on AIs / breast cancer patients on TAM / prostate cancer patients on any endocrine tx

#### 6. Are we interested in running treatment patterns of the breast and prostate cancer patients?
- would this be limited to endocrine treatments?
- stratified by age (given the difference in prescriptions by menospausal status)?



